Title

### 2018-07-31 thesis/paper/paper.tex
Added item requires statement

>>>>

\subsection{Item requires statement (Q21503247)}
The item requires statement constraint requires the pre-processing of all item statements. Additionally, inequality between all properties of item statements and the required property as well as between all values and the allowed values has to be established. It occurs in two varieties, depending on if allowed values have been specified or not. The predicate is defined as require\([2]\) denoting the statement and the required property. Without separators the conjunction is \(t = \text{tripleEDB}(S, I, P, V) \wedge \text{unequal}(\text{requiredPropertyConstant}, P)\).\\

If a set of allowed values \(A\) has been specified, a second set of require-rules have to be introduced with \(t = \text{tripleEDB}(S, I, \text{requiredPropertyConstant}, V) \wedge \text{unequal}(\{A\}, V)\). Note that the first set of rules is still required, since the preceding statements do not need to have the required property.\\

In both cases violations can be found with
\begin{equation*}
\begin{split}
\text{violation\_triple}&(S, I, \text{propertyConstant}, V) \leftarrow \\
&\text{tripleEDB}(S, I, \text{propertyConstant}, V) \wedge \\
&\text{tripleEDB}(O, I, P, X) \wedge \text{last}(O, I) \wedge \\
&\text{require}(O, \text{requiredPropertyConstant})
\end{split}
\end{equation*}
